\documentclass[main.tex]{subfiles}
\begin{document}

\href{https://www2.seas.gwu.edu/~simhaweb/quantum/modules/module3/module3.html}{Module 3: The Single Qubit}

\begin{enumerate}

\item[] \textbf{In-Class Exercise 1:} Suppose the qubit state is $|\psi\rangle=1+\rangle$ and the measurement basis is: $|w\rangle=\frac{\sqrt{3}}{2}|0\rangle-\frac{1}{2}|1\rangle$, and $\left|w^{\perp}\right\rangle=\frac{1}{2}|0\rangle+\frac{\sqrt{3}}{2}|1\rangle$. What are the possible output vectors, and with what probabilities do they occur? Start by expressing $|+\rangle$ in the $|w\rangle$, $\left|w^{\perp}\right\rangle$ basis by computing the coefficients $\langle w \mid+\rangle,\left\langle w^{\perp} \mid+\right\rangle$.

\item[] \textbf{In-Class Exercise 2:} What does the $X$ gate do to the state $|\psi\rangle=\alpha|0\rangle+\beta|1\rangle$ ?

\item[] \textbf{In-Class Exercise 3:} Derive the above result that applies $H$ to $|\psi\rangle=\alpha|0\rangle+\beta|1\rangle$. Also show that $H|\psi\rangle=\alpha|+\rangle+\beta|-\rangle$.

\item[] \textbf{In-Class Exercise 4:} Consider the two circuits below, each given the same input.

    \begin{enumerate}
        \item[1.] Write down the possible states of the outputs.
        \item[2.] Calculate the probabilities associated with each output state.
    \end{enumerate}

\item[] \textbf{In-Class Exercise 5:} Consider the following set up: (polariser 6)

What percentage of $|1\rangle$ photons arriving on the left reach the output? Work through your probability calculations as shown above.

\item[] \textbf{In-Class Exercise 6:}

    \begin{enumerate}
        \item[1.] What would go wrong if the S-H strings were exchanged before Bob performs qubit measurements?
        \item[2.] Write out the details of Case 2(B) above, explaining the details of measurement and probabilities.
    \end{enumerate}

\item[] \textbf{In-Class Exercise 7:} Show that with $a,|\psi\rangle$ and $\left|\psi^{\prime}\right\rangle$ defined above,

    \begin{enumerate}
        \item[1.] $|a|^{2}=1$
        \item[2.] $\left|\psi^{\prime}\right\rangle=a|\psi\rangle$
        \end{enumerate}

\item[] \textbf{In-Class Exercise 8:} Write down the two projector matrices $P_{v}, P_{v^{\perp}}$ for the general 2D basis $|v\rangle=a|0\rangle+b|1\rangle$, and $\left|v^{\perp}\right\rangle=b^{*}|0\rangle-a^{*}|1\rangle$ and check your calculations by showing $P_{v} P_{v^{\perp}}=0$.

\item[] \textbf{In-Class Exercise 9:} Suppose the qubit state is $|\psi\rangle=|+\rangle$ and the measurement basis is: $|w\rangle=\frac{\sqrt{3}}{2}|0\rangle-\frac{1}{2}|1\rangle$, and $\left|w^{\perp}\right\rangle=\frac{1}{2}|0\rangle+\frac{\sqrt{3}}{2}|1\rangle$. Apply the projective measurement approach:

    \begin{enumerate}
        \item[1.] Compute the projectors $P_{w}, P_{w^{\perp}}$.
        \item[2.] Apply the three steps, simplifying where possible.
    \end{enumerate}
    
    Confirm that you get the same results as in Exercise 1.

\item[] \textbf{In-Class Exercise 10:} Use the projector matrices for the basis and the numbers $\gamma_{1}=3, \gamma_{2}=5$ to construct the Hermitian. Then show that these are the eigenvalues with $k t+,|-\rangle$ as eigenvectors.

\item[] \textbf{In-Class Exercise 11:} Show that the Hadamard matrix can be written as $H=\frac{1}{\sqrt{2}}(|0\rangle\langle 0|+| 0\rangle\langle 1|+| 1\rangle\langle 0|-| 1\rangle\langle 1|)$ and then apply it to $|\psi\rangle=\alpha|0\rangle+\beta|1\rangle$.

\end{enumerate}
\end{document}